#Write an R program to create three vectors a, b, c with 5 integers. Combine the three vectors to become a 3×5 matrix where each column represents a vector. Print the content of the matrix. Plot a graph and label correctly.
```{r}
a <-c(5, 10, 15, 20, 25)
b <-c(2, 4, 6, 8, 10)
c <-c(1, 3, 5, 7, 9) 

x <- cbind(a, b, c)
x
plot(x)
```
#Write a R program to create a Data frames which contain details of 5 employees and display the details. (Name, Age, Role and Length of service).

```{r}
df <- data.frame (
  Name <-  c("Adam", "Joe", "Steve", "Sam", "Emily"),
  Age <-  c("35", "28", "29", "30", "25"),
  Role <-  c("Manager", "QC", "Customer Service", "HR", "Engineer"),
  Years_of_Service <-  c("10", "5", "8", "9", "2")
  )
df

```

#Import the GGPLOT 2 library and plot a graph using the qplot function. X axis is the sequence of 1:20 and the y axis is the x ^2. Label the graph appropriately. install.packages("ggplot2", dependencies = TRUE)
```{r}
install.packages("ggplot2", dependencies = TRUE)
require(ggplot2)
df <- data.frame (
  x <- c(1:20),
  y <- c(x^2)
)

qplot(x, y, data = df)
```

#Create a simple bar plot of five subjects
```{r}

a <- c("Red", "Orange", "Yellow", "Blue", "Green")
b <- c(10, 15, 12, 3, 20)

barplot(b, names.arg = a)

```

#Write a R program to take input from the user (name and age) and display the values.

```{r}
name <- readline("What is your name?")
age <- readline("How old are you?")

name
age
```

#Write a R program to create a sequence of numbers from 20 to 50 and find the mean of numbers from 20 to 50 and sum of numbers.
```{r}
x <- 20:50
x
sum(x)

mean(x)
```

#Write a R program to create a vector which contains 10 random integer values between -50 and +50
```{r}
sample(-50:50, 10)

```

